Efficient Handling of String-Number Conversion

### 2020-04-02 final-version/main.tex
change running example
typo

For ease of presentation, we  use the following toy example \changed{$$\Phi\!=\! \{``0"x\!=\! x``0", \sti{x} \!=\! \sti{y} ,|y|\!>\!|x|, 1000\!<\!|y| \}$$}
to explain the main ideas behind our decision procedure.  To make our terminology explicit: $\Phi$ states that \changed{$``0''$ concatenated with $x$ is the same as $x$ with $``0''$, the numeric value of the string $x$ is equivalent to that of $y$, $y$ is longer than $x$, and $y$ is longer than $1000$.  Notice that $\Phi$ is satisfiable. E.g., it has a model $x=``00"$ and $y=``0^{1002}"$}.

>>>>

For ease of presentation, we  use the following toy example \changed{$$\Phi\!=\! \{``0"x\!=\! x``0", \sti{x} \!=\! \sti{y} ,|y|\!>\!|x|, 1000\!<\!|y| \}$$}
to explain the main ideas behind our decision procedure.  To make our terminology explicit: $\Phi$ states that \changed{$``0"$ concatenated with $x$ is the same as $x$ with $``0"$, the numeric value of the string $x$ is equivalent to that of $y$, $y$ is longer than $x$, and $y$ is longer than $1000$ characteras.  Notice that $\Phi$ is satisfiable. E.g., it has a model $x=``00"$ and $y=``0^{1002}"$}.
